The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-02-10 src/ms.tex
Expand intro to new features

@@

\subsubsection*{New Features} \label{sec:core-features-new}

@@

New features come in various forms, from new submodules providing
wholly new capabilities, to larger additions to existing submodules,
to large rewrites of the interface of modules.  This range is spanned
by the four main features that entered the astropy core, which we
describe below.

>>>>

\defcitealias{astropy:2013}{Paper I}
\defcitealias{astropy:2018}{Paper II}

@@

\subsubsection*{New and Planned Features} \label{sec:core-features-new}

@@

New features come in various forms, from new submodules providing
wholly new capabilities, to larger additions to existing submodules,
to large rewrites of the interface of modules.  This range is spanned
by the five main new features that entered the astropy core since the
previous summary \citepalias{astropy:2018}.

New features present a particular difficulty for a mature package such
as \astropypkg, because by their nature they have not been tried out
much and it is difficult to know in advance what the best interface
will be, and hard to address all possible use cases in one go, even
within \astropypkg\ itself.  To give a sense of this, we include in
our descriptions how we hope the new features will evolve (realizing
that, in the end, in a user-driven project like \astropy, what happens
depends mostly on what is highest on the priority list of those that
have time to contribute).
